\Title

### 2020-11-26 manuscript/manuscript.tex
Add gradient boosting method to manuscript (#58)
Add description and mathematical background of gradient boosting method applied to equivalent sources.
Improve introduction to mention the new addition to the paper.
Fix minor issues, add a few more references, minor impovements.
Start adding boosting results to manuscript

Reducing the number of sources might help to lower the amount of computer
memory needed to fit their coefficients, although it may be not enough for
a very large set of observation points.
Even if we can greatly reduce the number of sources, having too many data
points would still produce a Jacobian matrix large enough that cannot fit in
memory.
This problem was already faced by other authors
\citep{
    mendonca1994,
    leao1989,
    li2010,
    barnes2011,
    oliveira2013,
    siqueira2017,
    jirigalatu2019
}.
The iterative method proposed by \citet{siqueira2017} needs equivalent sources
to be located beneath each observation point, so it cannot take advantage of
the block-averaged sources.
\citet{leao1989} perform the fitting simultaneously with the prediction, what
prevents us to use already fitted equivalent sources to make future
predictions. Besides the method is limited to interpolations on regular grids.
\citet{mendonca1994}
\citet{li2010}
\citet{barnes2011}
\citet{jirigalatu2019}

@@

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
See Figure~\ref{fig:flowchart} for a graphical illustration of this process.
This process is carried out on both ground and airborne synthetic surveys.

@@

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding RMS score, for both ground and synthetic surveys, respectively.
Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and synthetic surveys, respectively.

@@

@@

\section{Discussion}

>>>>

Reducing the number of sources might help to lower the amount of computer
memory needed to fit their coefficients, although it may be not enough for
a very large set of observation points.
Even if we can greatly reduce the number of sources, having too many data
points would still produce a Jacobian matrix large enough that cannot fit in
memory.
This problem was already faced by other authors
\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
jirigalatu2019}.
The iterative method proposed by \citet{siqueira2017} needs equivalent sources
to be located beneath each observation point, so it cannot take advantage of
the block-averaged sources.
\citet{leao1989} perform the fitting simultaneously with the prediction, what
prevents us to use already fitted equivalent sources to make future
predictions. Besides the method is limited to interpolations on regular grids.
% Add more discussion on why we won't apply any of the following methods
\citet{mendonca1994}
\citet{li2010}
\citet{barnes2011}
\citet{jirigalatu2019}

@@

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
This process is carried out on both ground and airborne synthetic surveys.
See Figure~\ref{fig:flowchart} for a graphical illustration of it.

@@

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding RMS score, for both ground and airborne synthetic surveys,
respectively.
Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and airborne synthetic surveys, respectively.

@@

\subsection{Discussion}

The RMS doesn't seem to depend on the choice of the depth strategy used to
locate the equivalent sources.
At first glance, the choice of a depth strategy doesn't seem to impact the
computational needs.
Nevertheless, when trying to find the set of parameters that produce the most
accurate predictions through a method like cross-validation, we need to fit the
source coefficients one time per every possible combination of parameters.
A depth strategy like the \emph{variable depth} needs a higher number of
parameters (depth, depth factor, K nearest) than \emph{constant depth} or
\emph{relative depth} (which takes only a depth parameter).
The addition of these new parameters makes the search of the best set more
computationally expensive: more parameters means increasing the dimensions of
the parameters space and thus increasing the number of possible combinations.
Therefore we would be more prone to choose a \emph{constant depth} or
a \emph{relative depth} when dealing with very large datasets in order to save
some computation time.

@@

\section{Performance of gradient boosted equivalent sources}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the more classical approach described on Section~\ref{sec:eql-inversion}.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data with different sets of
parameters. Then we compared each prediction to the target grid in order to get
the best prediction for each window size.
On every interpolation, block-averaged sources with relative depth are used
with a spacing of PUT-BLOCK-SPACING-HERE.
